---
title: "Data606_Week1HomeWord"
author: "Guang"
date: "September 9, 2018"
output: html_document
---


##Week1_home_Work

#Chapter 1 - Introduction to Data
#Graded: 1.8, 1.10, 1.28, 1.36, 1.48, 1.50, 1.56, 1.70 (use the library(openintro); data(heartTr) to load the data)


#1.8 Smoking habits of UK residents. A survey was conducted to study the smoking habits of UK residents. Below is a data matrix displaying a portion of the data collected in this survey.Note that “£” stands for British Pounds Sterling, “cig” stands for cigarettes, and “N/A” refers to a missing component of the data.58
sex age marital grossIncome smoke amtWeekends amtWeekdays
1 Female 42 Single Under£2,600 Yes 12 cig/day 12 cig/day
2 Male 44 Single £10,400 to £15,600 No N/A N/A
3 Male 53 Married Above£36,400 Yes 6 cig/day 6 cig/day
1691 Male 40 Single £2,600 to £5,200 Yes 8 cig/day 8 cig/day


(a) What does each row of the data matrix represent?
Each row of the data matrix repsents the value for the variables including sex ,age, marital ,grossIncome ,smoke ,amtWeekends ,amtWeekdays.

(b) How many participants were included in the survey?
1691 

(c) Indicate whether each variable in the study is numerical or categorical. If numerical, identify
as continuous or discrete. If categorical, indicate if the variable is ordinal.

Index: Numerical Continous.
Sex: Categorical.
Age: Numerical Discrete.
Marital Status: Categorical Ordinal 
grossIncom: Categorical Ordinal.
smoke: Categorical.
amtWeekend: Numerical Discrete.
amtWeekdays: Numerical Discrete

#11.10 
#Cheaters, scope of inference. Exercise 1.5 introduces a study where researchers studying the relationship between honesty, age, and self-control conducted an experiment on 160 children between the ages of 5 and 15. The researchers asked each child to toss a fair coin in private and to record the outcome (white or black) on a paper sheet, and said they would only reward children who report white. Half the students were explicitly told not to cheat and the others were not given any explicit instructions. Differences were observed in the cheating rates in the instruction and no instruction groups, as well as some diferences across children’s characteristics within each group.

(a) Identify the population of interest and the sample in this study.
Children between the ages of 5 and 15


(b) Comment on whether or not the results of the study can be generalized to the population, and if the findings of the study can be used to establish causal relationships.
The data is not probably generalized to the population because of the following reasons:
1. The sample size is too small
2. The method to choose subject was not clearly defined . Need to randomly pick.


#1.28 Reading the paper. Below are excerpts from two articles published in the NY Times:
#(a) An article titled Risks: Smokers Found More Prone to Dementia states the following:61 “Researchers analyzed data from 23,123 health plan members who participated in a voluntary exam and health behavior survey from 1978 to 1985, when they were 50-60 years old. 23 years later, about 25% of the group had dementia, including 1,136 with Alzheimer’s disease and 416 with vascular dementia. After adjusting for other factors, the researchers concluded that pack-aday smokers were 37% more likely than nonsmokers to develop dementia, and the risks went up with increased smoking; 44% for one to two packs a day; and twice the risk for more than two packs.”Based on this study, can we conclude that smoking causes dementia later in life? Explain your reasoning.

We can not conclude that the smoking causes dementia later in life, though we can find smoking is one of risk factor for demential. This is because the study was an observational study , not an experimental study. 



#(b) Another article titled The School Bully Is Sleepy states the following:62
#The University of Michigan study, collected survey data from parents on each child’s sleep habits and asked both parents and teachers to assess behavioral concerns. About a third of the students studied were identified by parents or teachers as having problems with disruptive behavior or bullying. The researchers found that children who had behavioral issues and those who were identified as bullies were twice as likely to have shown symptoms of sleep disorders.” A friend of yours who read the article says, “The study shows that sleep disorders lead to bullying in school children.” Is this statement justified? If not, how best can you describe the conclusion that can be drawn from this study?

The statement is not justfied . The better conclusion from the study is that children with sleep disorders are more likely to have bahavioural issues. 



#1.36 Exercise and mental health. A researcher is interested in the exects of exercise on mental health and he proposes the following study: Use stratified random sampling to ensure representativeproportions of 18-30, 31-40 and 41- 55 year olds from the population. Next, randomly assign half the subjects from each age group to exercise twice a week, and instruct the rest not to exercise. Conduct a mental health exam at the beginning and at the end of the study, and compare the results.
(a) What type of study is this?

Randomized Experiment


(b) What are the treatment and control groups in this study?
Treatment group: half the subjects from each age group with exercise 
Control group: half the subjects from each age group without exercise 

(c) Does this study make use of blocking? If so, what is the blocking variable?
Yes.  Age is the blocking variables 


(d) Does this study make use of blinding?
No. 

(e) Comment on whether or not the results of the study can be used to establish a causal relationship
between exercise and mental health, and indicate whether or not the conclusions can be generalized to the population at large.
No , because it is an observational study 

(f) Suppose you are given the task of determining if this proposed study should get funding. Would you have any reservations about the study proposal?
Yes. Study did not consider other factors which may affect mental health. 



#1.48 Stats scores. Below are the final exam scores of twenty introductory statistics students.
#57, 66, 69, 71, 72, 73, 74, 77, 78, 78, 79, 79, 81, 81, 82, 83, 83, 88, 89, 94
#Create a box plot of the distribution of these scores. The five number summary provided below may be useful.
#Min Q1 Q2 (Median) Q3 Max
#57 72.5 78.5 82.5 94



```{r}
student.grades <- c(57, 66, 69, 71, 72, 73, 74, 77, 78, 78, 79, 79, 81, 81, 82, 83, 83, 88, 89, 94)
summary (student.grades)
```
#boxplot
```{r}
boxplot(student.grades)
```

#1.50 
1.50 Mix-and-match. Describe the distribution in the histograms below and match them to
the box plots.
 A.  symmetric unimodal Distribution --> boxplot2 
 b.  multimodal  -->Boxplot(3)
 c.  Left skew unimodel --> Boxplot (1)
 
 
 
 
#1.56   Distributions and appropriate statistics, Part II. For each of the following, statewhether you expect the distribution to be symmetric, right skewed, or left skewed. Also specify whether the mean or median would best represent a typical observation in the data, and whetherthe variability of observations would be best represented using the standard deviation or IQR.Explain your reasoning.
(a) Housing prices in a country where 25% of the houses cost below $350,000, 50% of the houses
cost below $450,000, 75% of the houses cost below $1,000,000 and there are a meaningful
number of houses that cost more than $6,000,000.

Right skewed becuase of the the outlies ($6,000,000). The median and IQR would be the best measurements, since they are less subject to the influence of the outliers at the higher price. 


(b) Housing prices in a country where 25% of the houses cost below $300,000, 50% of the houses
cost below $600,000, 75% of the houses cost below $900,000 and very few houses that cost
more than $1,200,000.

Symmetric distribution. mean and standard deviation will be good measurements,because those data are normal distributed   

(c) Number of alcoholic drinks consumed by college students in a given week. Assume that most of these students don’t drink since they are under 21 years old, and only a few drink excessively.

Right Skewed distribution. The heavy drinks can be considered as outlies; The median and IQR would be the best measurements, since they are less subject to the influence of the outliers 


(d) Annual salaries of the employees at a Fortune 500 company where only a few high level executives earn much higher salaries than all the other employees.
 
Right skewed distribution. the salaries of high level executivespronounced can be considered as outlies ,  he median and IQR would be the best measurements, since they are less subject to the influence of the outliers 
 
 
 
 
#1.70 Heart transplants. The Stanford University Heart Transplant Study was conducted to determine whether an experimental heart transplant program increased lifespan. Each patient entering the program was designated an official heart transplant candidate, meaning that he was gravely ill and would most likely benefit from a new heart. Some patients got a transplant and some did not. The variable transplant indicates which group the patients were in; patients in the treatment group got a transplant and those in the control group did not. Another variable called survived was used to indicate whether or not the patient was alive at the end of the study. Of the 34 patients in the control group, 30 died. Of the 69 people in the treatment group, 45 died.74

(a) Based on the mosaic plot, is survival independent of whether or not the patient got a transplant?
Explain your reasoning.
The survival is not independent of whether or not the patient got a transplant, because the proportion of survivors in the treatment group is larger than in the control group
 


(b) What do the box plots below suggest about the efficacy (e↵ectiveness) of the heart transplant
treatment.
Yes, becuase both median and IQR in the exeperimental group is better than the control group 


(c) What proportion of patients in the treatment group and what proportion of patients in the control group died?

88% in the control group and 65% in the treatment group 

(d) One approach for investigating whether or not the treatment is e↵ective is to use a randomizationtechnique.

i. What are the claims being tested?
 H0: the heart transplant did not effect the survial time of the patients 
 H1: the heart transplant affected the survial time of the patients

ii. The paragraph below describes the set up for such approach, if we were to do it without
using statistical software. Fill in the blanks with a number or phrase, whichever is
appropriate.
We write alive on ** 28**  cards representing patients who were alive at the end of the study, and ** 75 ** dead on cards representing patients who were not. Then, we shu✏e these cards and split them into two groups:
one group of size ** 69 ** representing treatment, and another group of size **34**  representing control. We calculate the di↵erence between the proportion of dead cards in the treatment and control groups (treatment -control) and record this value. We repeat this 100 times to build a distribution centered at **0** . Lastly, we calculate the fraction of simulations where the simulated di↵erences in proportions are ** greater than or equal to the difference ** 
. If this fraction is low,we conclude that it is unlikely to have observed such an outcome by chance and that the null hypothesis should be rejected in favor of the alternative.



iii. What do the simulation results shown below suggest about the e↵ectiveness of the transplant program?
simulated differences in proportions
−0.25 −0.15 −0.05 0.05 0.15 0.25

The results suggest we should reject the null hypothesis , the heart transplant affected the survial time of the patients. 

 
